### 2015-09-05 cover_letter/cover_letter.tex
adjusts cover letter
customizes cover letter a bit more

\begin{letter}{Prof. A.K. Noor, Prof. B.H.V. Topping\\
Editors\\
Advances in Engineering Software}
%----------------------------------------------------------------------------------------
%       YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\address{Kathryn D. Huff\\
4155 Etcheverry Hall\\
MC 1730\\
Berkeley, CA 94720}

@@

This manuscript describes the fundamental concepts in the Cyclus nuclear fuel 
cycle simulator framework and its modeling ecosystem. These concepts and their 
implementations are described in the context of motivating challenges in 
nuclear fuel cycle simulation. Accordingly, the current capabilities of Cyclus 
are demonstrated for a range of representative fuel cycle scenarios including 
open (no recycling), closed (complete recycling), and modified open (some 
recycling) material routing schemes.

@@

Thank you for your consideration of this work. I expect it will be of interest
to a broad readership concerned with nuclear engineering, industrial and 
systems engineering, fuel cycle simulation, and agent-based computational 
methods. Please address all correspondence concerning this manuscript to me at 
UC Berkeley and feel free to correspond with me by e-mail.

>>>>

\begin{letter}{Professor A.K. Noor\\
Professor B.H.V. Topping\\
Editors, Advances in Engineering Software}
%----------------------------------------------------------------------------------------
%       YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\address{Kathryn D. Huff\\
2150 Shattuck Ave.\\
Suite 230\\
Berkeley, CA 94720}

@@

This manuscript describes the fundamental concepts in the Cyclus nuclear fuel 
cycle simulator framework and its modeling ecosystem. These concepts and their 
implementations are motivated by and described in the context of challenges in 
nuclear fuel cycle simulation. Accordingly, the current capabilities of Cyclus 
are demonstrated for a range of representative fuel cycle scenarios including 
open (no recycling), closed (complete recycling), and modified open (some 
recycling) material routing schemes.

@@

Thank you for your consideration of this work. I expect it will be of interest
to a broad readership concerned with applications of object-oriented simulation 
to engineering problems nuclear engineering, algorithms for engineering systems 
analysis, and agent-based computational methods. Please address all 
correspondence concerning this manuscript to me at UC Berkeley and feel free to 
correspond with me by e-mail.
